### 2019-01-13 papers/journal/experiments.tex
small changes

%We encode the problem using CBMC C-language front-end (CFE) interface with some special annotations called \textit{assumes} and \textit{assertions}.
%
%These annotations express constraints on the model and properties to be checked. 
%	
The vesicle transport network was modelled as a non-deterministic C-program manipulating an annotated graph. 
%
The special annotations \textit{assumes} and \textit{assertions} of CBMC's front end were used to express constraints on the model and properties to be checked. 
%
%The fusion rules and steady state properties were expressed as constraints using special annotations \textit{assumes}. 
%		
%The correspondence relationship between connectedness conditions and steady state were expressed as annotations \textit{assertions} to be checked. 
Using the tool's interface user can select the variation of the VTS, connectivity of the graph and other required parameters like an exploration depth.
%
The {\sattool} verifies the properties by first converting the constraints and properties into a Boolean formula and determine the satisfiability of the formula with the help of a SAT solver backend.
%
The satisfying model is translated into a readable format and in case of a violation, the tool produces a readable counterexample.
%  following steps:
%	\begin{itemize}
%	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
%depth iff the Boolean formula is valid.
%	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
%an assignment to the variables of the model, that is a witness to the violation of the property.
%	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}.
% the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\textbf{{\smttool} (SMT based tool)}:
The recursive encoding (presented in section 6.1)  
%We have implemented the encodings 
for each variant is implemented in {\smttool}.
%
The tool is based on industrial strength SMT solver, Z3. 
%
The tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that respects the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and represent a visual output to the user in form of coloured annotated graph. 
%
%We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
%

@@

\textbf{{\ourtool} (QBF based synthesis tool):}
\input{synth-table}
We have implemented the synthesis encodings (presented in section 6.6) in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can not only synthesize the discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

\subsection{Results}
The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.

@@

The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
%
%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
The steady-state constraint requires that structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For more constrained regulation models
(including the case where SNAREs are always active) we did not find any possible graphs
representing steady state vesicle transport networks. 
%
This strongly suggests (but does not
prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

>>>>

%We encode the problem using CBMC C-language front-end (CFE) interface with some special annotations called \textit{assumes} and \textit{assertions}.
%
%These annotations express constraints on the model and properties to be checked. 
%	
The vesicle transport network was modelled as a non-deterministic C-program manipulating an annotated graph. 
%
The special annotations \textit{assumes} and \textit{assertions} of CBMC's front end were used to express constraints on the model and properties to be checked. 
%
%The fusion rules and steady state properties were expressed as constraints using special annotations \textit{assumes}. 
%		
%The correspondence relationship between connectedness conditions and steady state were expressed as annotations \textit{assertions} to be checked. 
Using the tool's interface user can select the variation of the VTS, connectivity of the graph and other required parameters like an exploration depth.
%
The {\sattool} verifies the properties by first converting the constraints and properties into a Boolean formula and determine the satisfiability of the formula with the help of a SAT solver backend.
%
The satisfying model is translated into a human readable format and in case of a violation, the tool produces a readable counterexample.
%  following steps:
%	\begin{itemize}
%	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
%depth iff the Boolean formula is valid.
%	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
%an assignment to the variables of the model, that is a witness to the violation of the property.
%	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}.
% the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\textbf{{\smttool} (SMT based tool)}:
The recursive encoding (presented in section 6.1)  
%We have implemented the encodings 
for each variant is implemented in {\smttool}.
%
The tool is based on industrial strength SMT solver, Z3. 
%
The tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that follows the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and represent a visual output to the user in form of coloured annotated graph. 
%
%We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
%

@@

\textbf{{\ourtool} (QBF based synthesis tool):}
\input{synth-table}
We have implemented the synthesis encodings (presented in section 6.6) in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can synthesize the queries discussed earlier and also their combinations.
%The tool can not only synthesize the discussed queries, but also their combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

\subsection{Results}
The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\qbftool} and in table~\ref{tab:synth-graph} for~{\ourtool}.

@@

The minimal connectivity results for each variation of the existential condition are presented in table~\ref{tab:smt-grph}.
%
%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
The steady-state constraint requires that structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
%(including the case where SNAREs are always active) we did not find any possible graphs representing stable vesicle transport networks. 
%
This hints that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof. 
%This strongly suggests (but does not prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

### 2019-01-13 papers/journal/related.tex
small changes

The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification, equivalence checking, automatic test generation,
AI planning, scheduling and program synthesis. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

One of the prominent areas of application of SAt/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
We have extended the application of SAT and SMT solvers to the most complex Biological transport network (VTS)~\cite{mani2016stacking,shukla}.

>>>>

\todo{Add references}
The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification, equivalence checking, automatic test generation,
AI planning, scheduling and program synthesis. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

One of the prominent areas of application of SAT/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
The gene regulatory network question is encoded into a Boolean satisfiability problem and then with the help of a SAT and SMT solvers solve the generated formula. 
% 
We have extended the application of SAT and SMT solvers to a more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.
